Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Speculatively remove Cloud-Entry.
I think we'll need the space and I don't think development of that tool
got very far.

Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
It also uses App Engine, but via a socket API rather than a URL fetch API,
in order to support protocols other than HTTP and HTTPS.
Cloud-Entry has the same NAT problem as flash proxy,
because the proxy tries to connect back to the client with a socket.
App Engine kills web requests (and their associated socket connections)
when they take longer than 60~seconds,
so users must reconnect at least that often.

>>>>

% Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
% It also uses App Engine, but via a socket API rather than a URL fetch API,
% in order to support protocols other than HTTP and HTTPS.
% Cloud-Entry has the same NAT problem as flash proxy,
% because the proxy tries to connect back to the client with a socket.
% App Engine kills web requests (and their associated socket connections)
% when they take longer than 60~seconds,
% so users must reconnect at least that often.
